The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-04-02 VegOzone.tex
Updated plots and text in accordance.

\subsubsection{Temperature and precipitation}
\label{subsubsec:clim_temp_prec}
\begin{figure}[t]
  \includegraphics[width=8.3cm]{climatediagram}
  \caption{Climate diagram following Walter and Lieth. The diagram is based on climatological data for Svanvik/Pasvik (1992--2017) downloaded from LandbruksMeteorologiske Tjeneste. Monthly average temperatures (red line) are displayed with standard error of mean as error band. Average monthly accumulated precipitation (blue bars) is shown with standard deviation of mean as error bars. Months with average temperatures below freezing are denoted with a star.}
  \label{fig:climatediagram}
\end{figure}

@@

\subsection{2018/19 anomalies}
\begin{itemize}
\item temperature
\item precipitation
\item ozone
\end{itemize}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{plot_temperature_anomalies_svanvik}
  \caption{{\bf TODO: Replace by analysis based on Svanvik observed climatology.} Time series over the past 6 years of (a) temperature observed at Svanhovd and climatology derived from CRU bias-corrected reanalysis; (b) Student's t-test of temperature. The summer of 2018 has been significantly warmer on the $2-4\,\sigma$ level. The summer of 2019 was fairly average but on the colder side.}
  \label{fig:plot_temperature_anomalies_svanvik}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{plot_precipitation_anomalies_svanvik}
  \caption{{\bf TODO: Replace by analysis based on Svanvik observed climatology.} Time series over the past 6 years of (a) precipitation observed at Svanhovd and climatology derived from CRU bias-corrected reanalysis; (b) Student's t-test of precipitation.}
  \label{fig:plot_precipitation_anomalies_svanvik}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{global_rad_signific}
  \caption{Global irradiance at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. (a) 2018; (b) 2019. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviation are indicated in the respective corners (right upper/ right lower).}
  \label{fig:global_rad_signific}
\end{figure}

>>>>

\subsubsection{Temperature, precipitation, and global irradiance}
\label{subsubsec:clim_temp_prec}
\begin{figure}[t]
  \includegraphics[width=8.3cm]{climatediagram}
  \caption{Climate diagram following Walter and Lieth. The diagram is based on climatological data for Svanvik/Pasvik (1992--2017) downloaded from LandbruksMeteorologiske Tjeneste. Monthly average temperatures (red line) are displayed with standard error of mean as error band. Average monthly accumulated precipitation (blue bars) is shown with standard deviation of mean as error bars. Months with average temperatures below freezing are denoted with a star.}
  \label{fig:climatediagram}
\end{figure}

@@

\subsection{2018/19 anomalies}
\label{subsec:anomalies}

\subsubsection{Temperature, precipitation, and global irradiance}
\label{subsubsec:anomal_tpq}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{temperature_signific}
  \caption{Temperature at Svanvik. Percentage of days warmer/colder than $\pm 1\,\sigma$ from climatological mean displayed for each month. (a) 2018; (b) 2019. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/ right lower). The summer of 2018 was significantly warmer than average, especially May and July. The summer of 2019 was fairly average but significantly warmer than average in April and colder in July/August.}
  \label{fig:plot_temperature_anomalies_svanvik}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{precipitation_signific}
  \caption{Precipitation at Svanvik. Percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from climatological mean displayed for each month. (a) 2018; (b) 2019. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/ right lower). The summer of 2018 was significantly drier than in 2019.}
  \label{fig:plot_precipitation_anomalies_svanvik}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{global_rad_signific}
  \caption{Global irradiance at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. (a) 2018; (b) 2019. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/ right lower). In summer 2018 (May/July), gobal irradiance was significantly higher than on average, while 2019 was generally an average year.}
  \label{fig:global_rad_signific}
\end{figure}

\subsubsection{Ozone}
\label{subsubsec:anomal_ozone}

@@
